---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Taelor Anderson"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?

```{r q1}
covid_data_count  |> 
  filter(state == "FL") |>
ggplot(aes(x=race, y=Cases,fill=race))+geom_boxplot(alpha=0.3)

```

The median of the white population of cases is highest in the Latinx population, closely followed by the White population, then the black population, with other coming in last. 

2. Are there any conclusions you can draw?

There appears to be a significant difference between the ranges of cases by race, as the Asian population has far less cases than the other race in Alabama.  

3. What were you not able to do due to not having the R knowledge?

I cannot change the color scheme from this weird rainbow palette. I also want to be able to select only certain states to model but I don't know how to filter it to be more than 1 but less than all 50. I also wanted to order the plots so that "Total" was at the end and couldn't figure that out. 


4. What other data would be useful to better understand this data?

Data about rate of re-infection could be cool to look at, although I'm not sure how many had been reinfected at this stage in the pandemic. I would also LOVE to compare this to data from 2021 because I love an "over time" comparison.
